ethan_analysis

### 2022-12-09 ethan_analysis.Rmd

```{r}
#install.packages("tidymodels")
#install.packages("fs")
#install.packages("caret")
#install.packages("caTools")
#install.packages("leaps")
#install.packages("glmnet")
#install.packages("pls")
#install.packages("forecast")
#install.packages("plyr")
#install.packages("readr")
#install.packages("repr")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}

#setwd("~/Desktop/DSCI/DSCI445/Project")
library(tidyverse)
library(ggplot2)
library(dplyr)
library(caret)
library(leaps)
library(caTools)
library(tidymodels)
library(glmnet)
library(pls)
library(forecast)
library(GGally)
library(plyr)
library(readr)
library(repr)

@@

```{r}
as_data_frame(rbind(amtrain_log,
      amr_train,
      aml_train,
      amtest_log,
      amr_test,
      aml_test)) %>%
    mutate(model = c('Linear Train Error',  'Ridge Train Error', 'Lasso Train Error',  'Linear Test Error','Ridge Test Error',  'Lasso Test Error')) %>%
    select(model, RMSE, Rsquared)
```

@@

```{r}
as_data_frame(rbind(awtrain_log,
      awr_train,
      awl_train,
      awtest_log,
      awr_test,
      awl_test)) %>%
    mutate(model = c('Linear Train Error',  'Ridge Train Error', 'Lasso Train Error',  'Linear Test Error','Ridge Test Error',  'Lasso Test Error')) %>%
    select(model, RMSE, Rsquared)
```
--------------------------------------------------------------------------------
## concave.points_mean

@@

  # Model performance metrics
data.frame(
  RMSE = RMSE,
  Rsquare = R_square)

@@

# Prediction and evaluation on train data
predictions_train <- predict(ridge_reg, s = optimal_lambda, newx = x)
cvptsm_train <- eval_results(y_train, predictions_train, trainTot)

# Prediction and evaluation on test data
predictions_test <- predict(ridge_reg, s = optimal_lambda, newx = x_test)
cvptsm_test <- eval_results(y_test, predictions_test, testTot)

print(cvptsm_train)
print(cvptsm_test)
```

@@

predictions_train <- predict(lasso_model, s = lambda_best, newx = x)
cvptsm_train <- eval_results(y_train, predictions_train, trainTot)

predictions_test <- predict(lasso_model, s = lambda_best, newx = x_test)
cvptsm_test <- eval_results(y_test, predictions_test, testTot)

print(cvptsm_train)
print(cvptsm_test)
```

@@

# Prediction and evaluation on train data
predictions_train <- predict(ridge_reg, s = optimal_lambda, newx = x)
rw_train <- eval_results(y_train, predictions_train, trainTot)

# Prediction and evaluation on test data
predictions_test <- predict(ridge_reg, s = optimal_lambda, newx = x_test)
rw_test <- eval_results(y_test, predictions_test, testTot)

print(rw_train)
print(rw_test)
```

@@

predictions_train <- predict(lasso_model, s = lambda_best, newx = x)
rw_train <- eval_results(y_train, predictions_train, trainTot)

predictions_test <- predict(lasso_model, s = lambda_best, newx = x_test)
rw_test <- eval_results(y_test, predictions_test, testTot)

print(rw_train)
print(rw_test)
```

>>>>

```{r}
#install.packages("tidymodels")
#install.packages("fs")
#install.packages("caret")
#install.packages("caTools")
#install.packages("leaps")
#install.packages("glmnet")
#install.packages("pls")
#install.packages("forecast")
#install.packages("plyr")
#install.packages("readr")
#install.packages("repr")
install.packages("kableExtra")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}

#setwd("~/Desktop/DSCI/DSCI445/Project")
library(tidyverse)
library(ggplot2)
library(dplyr)
library(caret)
library(leaps)
library(caTools)
library(tidymodels)
library(glmnet)
library(pls)
library(forecast)
library(GGally)
library(plyr)
library(readr)
library(repr)
library(knitr)
library(kableExtra)

@@

```{r}
table_am <- as_tibble(rbind(amtrain_log,
      amtest_log,
      amr_train,
      amr_test,
      aml_train,
      aml_test)) %>%
    mutate(model = c('Linear Train Error',  'Linear Test Error','Ridge Train Error', 'Ridge Test Error', 'Lasso Train Error', 'Lasso Test Error')) %>%
    select(model, RMSE, Rsquared)
table_am %>% 
  kbl(digits = 5 ) %>% 
  kable_styling(bootstrap_options = "striped")
```

@@

```{r}
table_aw <- as_tibble(rbind(awtrain_log,
      awtest_log,
      awr_train,
      awr_test,
      awl_train,
      awl_test)) %>%
    mutate(model = c('Linear Train Error',  'Linear Test Error','Ridge Train Error', 'Ridge Test Error', 'Lasso Train Error', 'Lasso Test Error')) %>%
    select(model, RMSE, Rsquared)
table_aw %>% 
  kbl(digits = 5 ) %>% 
  kable_styling(bootstrap_options = "striped")
```

--------------------------------------------------------------------------------
## concave.points_mean

@@

@@

# Prediction and evaluation on train data
predictions_train <- predict(ridge_reg, s = optimal_lambda, newx = x)
cvptsmr_train <- eval_results(y_train, predictions_train, trainTot)

# Prediction and evaluation on test data
predictions_test <- predict(ridge_reg, s = optimal_lambda, newx = x_test)
cvptsmr_test <- eval_results(y_test, predictions_test, testTot)

print(cvptsmr_train)
print(cvptsmr_test)
```

@@

predictions_train <- predict(lasso_model, s = lambda_best, newx = x)
cvptsml_train <- eval_results(y_train, predictions_train, trainTot)

predictions_test <- predict(lasso_model, s = lambda_best, newx = x_test)
cvptsml_test <- eval_results(y_test, predictions_test, testTot)

print(cvptsml_train)
print(cvptsml_test)
```

```{r}
table_am <- as_tibble(rbind(cvptsm_train_log,
      cvptsm_test_log,
      cvptsmr_train,
      cvptsmr_test,
      cvptsml_train,
      cvptsml_test)) %>%
    mutate(model = c('Linear Train Error',  'Linear Test Error','Ridge Train Error', 'Ridge Test Error', 'Lasso Train Error', 'Lasso Test Error')) %>%
    select(model, RMSE, Rsquared)
table_am %>% 
  kbl(digits = 5 ) %>% 
  kable_styling(bootstrap_options = "striped")
```

@@

# Prediction and evaluation on train data
predictions_train <- predict(ridge_reg, s = optimal_lambda, newx = x)
rwr_train <- eval_results(y_train, predictions_train, trainTot)

# Prediction and evaluation on test data
predictions_test <- predict(ridge_reg, s = optimal_lambda, newx = x_test)
rwr_test <- eval_results(y_test, predictions_test, testTot)

print(rwr_train)
print(rwr_test)
```

@@

predictions_train <- predict(lasso_model, s = lambda_best, newx = x)
rwl_train <- eval_results(y_train, predictions_train, trainTot)

predictions_test <- predict(lasso_model, s = lambda_best, newx = x_test)
rwl_test <- eval_results(y_test, predictions_test, testTot)

print(rwl_train)
print(rwl_test)
```

```{r}
table_am <- as_tibble(rbind(rw_train_log,
      rw_test_log,
      rwr_train,
      rwr_test,
      rwl_train,
      rwl_test)) %>%
    mutate(model = c('Linear Train Error',  'Linear Test Error','Ridge Train Error', 'Ridge Test Error', 'Lasso Train Error', 'Lasso Test Error')) %>%
    select(model, RMSE, Rsquared)
table_am %>% 
  kbl(digits = 5 ) %>% 
  kable_styling(bootstrap_options = "striped")
```
